%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
% \documentclass[a4paper]{article}

\usepackage{helvet} % Default font is the helvetica postscript font
% \usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
% \usepackage{baskervald}

\usepackage[brazil]{babel}
\usepackage[utf8]{inputenc}
% \usepackage[tmargin=2.2cm, bmargin=2.2cm, lmargin=2.2cm, rmargin=2.2cm]{geometry}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=blue,
    urlcolor=blue
}

\usepackage{calc}

\usepackage{enumitem}

% A4 tem 8.267in x 11.692in

% resumewidth default é 6.5

% nt = nr - vr + vt

\def \mymargin{0.4in}
\def \mymarginright{0.85in}
\def \mysectionwidth{70pt}

\newsectionwidth{\mysectionwidth}

\def \newresumewidth{8.267in - \mymargin - \mymarginright}
\def \newtextwidth{\newresumewidth - \mysectionwidth}

\usepackage[margin=\mymargin, top=0.7in, a4paper]{geometry}

\setlength{\textwidth}{\newtextwidth}
% \setlength{\textwidth}{5.1in}
\setlength{\resumewidth}{\newresumewidth}

\newcommand{\sbt}{\,\begin{picture}(-1,1)(-2,-3)\circle*{2}\end{picture}\ }

\def \divspace{6pt}
\def \myitemback{0.55cm}
\def \myitemsep{0pt}

% \def \mypositionface{\sc}
\def \mypositionface{\sl}
% \def \mypositionface{\it}
% \def \mypositionface{\uppercase}
% \def \mypositionface{\lfseries}
% \def \mypositionface{\mdseries}

\def \myprojectface{\it}

\def \myorgface{\sc}
% \def \myorgface{\sl}
% \def \myorgface{\it}
% \def \myorgface{\uppercase}
% \def \myorgface{\lfseries}
% \def \myorgface{\mdseries}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\huge\uppercase{Mikail Campos Freitas}} % Your name at the top

\moveleft.5\hoffset\centerline{\rule{2.5in}{.2pt}}\smallskip % Your address

\moveleft.5\hoffset\centerline{Addr. Alameda Itupiranga, 309, Saúde} % Your address
\moveleft.5\hoffset\centerline{Brazil, São Paulo, SP - 04294-090}
\moveleft.5\hoffset\centerline{Home. +55 (11) 2352-2157 / Mobile. +55 (11) 97288-9984}
\moveleft.5\hoffset\centerline{contact@mikail.io / Website. \href{http://mikail.io}{http://mikail.io}}
\vskip-3.5ex

%-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------

\begin{resume}
\section{OBJECTIVES \hspace{\divspace} }

To learn new technologies and to expand my knowledge and skills through the pursuit and overcoming of challenges. To exchange experience with other professionals and becoma a better one myself.

%-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\section{EDUCATION \hspace{\divspace} }

{\myprojectface Bachelor of Computer Science} \hfill 2008 — 2012 \\
{\myorgface University of São Paulo}'s {\myorgface Institute of Mathematics and Statistics} (IME - USP)\\
Course Completion Assignment: {\sl Solving the PSAT problem with assistance of the free software MiniSat} \href{http://www.ime.usp.br/~cef/mac499-12/monografias/rec/mikail/index.html}{[link]}

%-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\section{COLLEGE \hspace{\divspace} }
\section{PROJECTS \hspace{\divspace} }
\vskip-2.5ex  % mágica da gambi que faz o texto ser renderizado uma linha pra cima

{\myprojectface Simple 2D game with C} \hfill 2010 (4 months) \\
{\mypositionface Lead Programmer} \\
2D game with simple physics where two players compete with each other for points for saving survivors from a shipwreck. Made with C and the Allegro multimedia library (graphics and input). \href{http://mikail.io/castaway/}{[link]}

{\myprojectface Augmented reality 3D game with ActionScript 3} \hfill 2010 (6 months) \\
{\mypositionface Solo Programmer} \\
Augmented reality 3D puzzle game where the player has to make a ball reach the final destination through obstacles in the virtual inside of a cube. Made with ActionScript 3 and the following libraries: JigLib for 3D physics, Papervision3D for 3D graphics, FLARManager for augmented reality. \href{http://mikail.io/ar_game/}{[link]}

{\myprojectface First Person Walking Simulator with C++ and OpenGL} \hfill 2012 (5 months) \\
{\mypositionface Solo Programmer} \\
Interactive simulator with basic physics enabling the user to walk around the buildings of the USP's Institute of Mathematics and Statistics (outside only). Made solely with C++ and OpenGL. \href{http://mikail.io/walker/}{[link]}

%-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\section{PERSONAL \hspace{\divspace} }
\section{PROJECTS \hspace{\divspace} }
\vskip-2.5ex  % mágica da gambi que faz o texto ser renderizado uma linha pra cima

{\myprojectface Multiplatform game with C++} \hfill 2012 — present (very sparse) \\
{\mypositionface Solo Programmer} \\
2D platform game with it's own physics and lightning effects egines. Multiplatform project that utilizes OpenGL, GLSL and the SFML (C++) library for input and graphics management.
Currently has a version in {\it very} early development for Mac OS X. Windows version in progress.

%-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\section{EXPERIENCE \hspace{\divspace} }

{\mypositionface Programmer} \hfill 2013 — 2014 \\
{\myorgface VTX Brasil}

\begin{itemize}[itemsep=\myitemsep,leftmargin=\myitemback]
\item[\sbt] Development of IM and video call application for iOS. (6 months)
\item[\sbt] Development of multiple-device split video playback application for Android. (3 months)
\end{itemize}

{\mypositionface Lead Programmer} \hfill 2014 — present \\
{\myorgface VTX Brasil}

\begin{itemize}[itemsep=\myitemsep,leftmargin=\myitemback]
\item[\sbt] Product conception and direction of development.
\item[\sbt] Head of development of iOS application for engagement in retail through innovative technologies. (14 months)
\end{itemize}

%-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\section{SKILLS \hspace{\divspace} }

- {\sl Languages}: \\
\setlength\tabcolsep{2pt}
\begin{tabular}{l l}
\hspace*{1.5em}{\it Fluent}:& Objective-C, C, regex \\
\hspace*{1.5em}{\it More Familiar}:& Python, C++, Java, Scheme, Erlang, ActionScript 3, \LaTeX, GLSL \\
\hspace*{1.5em}{\it Less Familiar}:& CUDA, Assembly, Prolog, Swift, Smalltalk, Pascal, Bash \\
\end{tabular}
\\
- {\sl Frameworks, libraries and technologies:} \\
\hspace*{1.5em}iBeacon, SFML, Allegro, NumPy, JigLib, Papervision3D, FLARManager, AllJoyn, Vuforia, \\
\hspace*{1.5em}OpenCV, Liblinphone, Augmented Reality
\\
- {\sl Softwares e tools:} \\
\hspace*{1.5em}Git (advanced), gnuplot, Xcode, Eclipse, ADT, FlashDevelop, Sublime Text, TextMate, vim
\\
- Intermediate knowledge of OpenGL and shaders \\
- Development in Ubuntu and Debian systems (7 years) and Mac OS X (5 years) \\
- Intermediate knowledge of cryptography \\
- Intermediate-advanced image editing in Adobe Photoshop \\
- Fluent english, basic-intermediate japanese, basic spanish\\\\

%-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------

\section{AWARDS \hspace{\divspace} }

- Bronze medal in the {\sl Informatics Brazilian Olympics} (2007) \\
- Silver medal in the {\sl Astronomy Brazilian Olympics} (2006) \\
- Silver medal in the {\sl Astronomy Brazilian Olympics} (2007) \\
- Honorable Mention in the {\sl Physics Brazilian Olympics} (2007) \\
- Progressed to the last stage of recruitment by the Microsoft Corporation in IME - USP (2012)

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}